Modern Graph Generators: A Survey

### 2018-09-14 generators_analytics.tex
Adding of short introductions/conclusions etc.

\TODO{A short intro.}

>>>>

Graph analytics, especially in the context v Big Data, is a popular area of studying interesting structural specifics of graphs, usually various types of networks.  Hence, the respective benchmarks and graph data generators developed for the purpose of testing graph analytics tools (such as, e.g.,  PowerGraph~\cite{Gonzalez:2012:PDG:2387880.2387883} or Parallel Graph analytiX~\cite{Sevenich:2016:UDL:3007263.3007265}) have to focus mainly on graphs with complex structures.

### 2018-09-14 generators_community_detection.tex
Adding of short introductions/conclusions etc.

\subsubsection{Graphs Generators for Benchmarking Community Detection Algorithms}
\label{sec:generators_community_detection}

Community detection is one of the many graph analytics algorithms typically used on domains such as social networks or bioinformatics. Communities are groups of vertices that are highly connected among them, while being scarcely connected to the rest of the graph. Such communities emerge from the fact that real graphs are not random, but follow real-world dynamics that make similar entities to have a larger probability to be connected. As a consequence, detected communities are used to reveal vertices with similar characteristics, for instance to discover functionally equivalent proteins in protein-protein interaction networks, or persons with similar interests in social networks. Such applications have made community detection a hot topic during the last fifteen years with tens of developed algorithms and detection strategies.\TODO{references} In order to compare the quality of the different proposed techniques, one needs graphs with \emph{reference communities}, that is, communities known beforehand. Since it is very difficult to have large real graphs with reference communities (mainly because these would require a manual labeling), graphs for benchmarking community detection algorithms are typically generated synthetically.

>>>>

\subsubsection{Community Detection}
\label{sec:generators_community_detection}

Community detection is one of the many graph analytics algorithms typically used on domains such as social networks or bioinformatics. Communities are groups of vertices that are highly connected among them, while being scarcely connected to the rest of the graph. Such communities emerge from the fact that real graphs are not random, but follow real-world dynamics that make similar entities to have a larger probability to be connected. As a consequence, detected communities are used to reveal vertices with similar characteristics, for instance to discover functionally equivalent proteins in protein-protein interaction networks, or persons with similar interests in social networks. Such applications have made community detection a hot topic during the last fifteen years with tens of developed algorithms and detection strategies~\cite{doi:10.1002/wics.1403,Kim:2015:CDM:2854006.2854013}. In order to compare the quality of the different proposed techniques, one needs graphs with \emph{reference communities}, that is, communities known beforehand. Since it is very difficult to have large real graphs with reference communities (mainly because these would require a manual labeling), graphs for benchmarking community detection algorithms are typically generated synthetically.

### 2018-09-14 introduction.tex
Adding of short introductions/conclusions etc.

To conclude the comparative study and provide a comprehensive view of the
field,  we also discuss open challenges and missing requirements of modern
graph generators in view of identifying their future extensions to new emerging fields.

>>>>

To conclude the comparative study and provide a comprehensive view of the
field,  we also overview the most popular real-world data sets used in the respective covered areas and discuss open challenges and missing requirements of modern
graph generators in view of identifying their future extensions to new emerging fields.
